```{r}
library(tidyverse)
library(ggthemes)
library(readxl)
library(writexl)

#prints <- read_excel("C:/Users/Ryan/Coding Projects/KDL Project/3D Printing analysis/Data/EGR KDL Master 3D Printing List.xlsx")

#Loading in the excel file when 3d printing analysis is set as working directory 
prints <- read_excel("Data/Example data.xlsx")


#Filtering the data based on date 
#prints <- prints %>% filter(completion_time >= as.Date("2023-04-13"))
```


# Print distribution (pie chart)
```{r}
#Wrangling the data to be in pie chart format

pies <- prints %>% count(print)
pies$percent_NOP <- pies$n / sum(pies$n) * 100
pies$print <- as.character(pies$print)

pies1 <- pies %>% head(20)


# Create the pie chart
ggplot(pies1, aes(x = "", y = percent_NOP, fill = print)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar(theta = "y") +
  
  geom_text(aes(label = paste0(round(percent_NOP), "%")), 
            position = position_jitterdodge(jitter.width = 0.2, dodge.width = .8), 
            size = 4) +
  #geom_text(aes(label = paste0(round(percent_NOP), "%")), position = position_stack(vjust = 0.5)) +
  #scale_fill_brewer(palette = "Dark2", name = "Number of People per Group") +
  
  labs(
    title = "Study Rooms Requests by Group Size"
  ) +
  
  theme_void()


#ggsave(one, file = "pie12.png")
```


# Print distribution (bar chart)
```{r}
#Still really difficult to see graphically so will make a table 

ggplot(prints, aes(x = print)) +
  geom_bar()

table_prints <- table(prints$print)

table_counts_df <- as.data.frame(table_prints)

# Rename the columns in the data frame
colnames(table_counts_df) <- c("Print", "Count")

table_counts_df <- arrange(table_counts_df, desc(Count))

print(table_counts_df)

#write_xlsx(table_counts_df, "print distribution_after.xlsx")
```


#color distribution
```{r}
#might be useful later when coloring each bar chart according to it's actual color

colors_list <- unique(prints$color)

#might want to explore making color a factor variable if I want a specific order for my bar chart 
#prints$color <- factor(prints$color, ordered = FALSE)

# If we want to order the colors on the bar chart by count
# prints$color <- factor(prints$color, levels = names(sort(table(prints$color), decreasing = TRUE)))

ggplot(prints, aes(x= color, fill = color)) +
  geom_bar(show.legend = FALSE, color = "black") +
  
  labs(title = "Color Distribution for 3D Prints",
       y = "Number of Prints",
       x = NULL,
       subtitle = "After Online Form (after 6/5/23)") +
  
  scale_y_continuous(
      breaks = seq(0, 14, by = 2),
      #minor_breaks = seq(0, 22, by = 1),
      limits = c(0, 14)) +
  
  #Archive print list color values 
  #scale_fill_manual(values = c("black", "blue", "darkgrey", "green", "lightgrey", "pink", "hotpink3", "mediumpurple4", "red", "ivory1", "indianred1", "yellow")) + 
  
  #Current print list color values 
#scale_fill_manual(values = c("black", 'blue', 'green', 'darkgrey', 'orange', 'lightpink', 'red', 'floralwhite', 'yellow')) + 

  scale_fill_manual(values = c( 'blue', 'green',  'orange')) + 

  
  theme_clean() +
  
  theme(plot.subtitle = element_text(size = 10),
        axis.text.x = element_text(angle = 30, hjust = 1))
  
  #In case we need to rotate the x axis labels or put in a minor line  
  #theme(axis.text.x = element_text(angle = 45, hjust = 1),
        #panel.grid.minor.y = element_line(color = "gray", linetype = "dotted"))


#ggsave(one, file = "print distribution_after.png")
```


#Finding the time is takes to go from print requested to patron contacted 
```{r}
#I filter out ID number 210 here because that was an outlier for contacting the person 

prints <- prints %>% mutate(turnaround = as.Date(contacted_date) - as.Date(completion_time)) %>% filter(ID != 210)

#looking at turnaround time as a difftime variable

class(prints$turnaround)

summary(prints$turnaround, na.rm = TRUE)

mean(prints$turnaround, na.rm = TRUE)


#Changing turnaround variable to a numeric variable for a more standard analysis
prints$turnaround <- as.numeric(prints$turnaround)

summary(prints$turnaround, na.rm = TRUE)

mean_turnaround <- mean(prints$turnaround, na.rm = TRUE)

print(paste0("On average, it took us ", round(mean_turnaround, 2), " days to complete a patrons print once they requested it"))
```


#Calculating invalid email rate 
```{r}
emails_fails <- sum(prints$invalid_email == "X", na.rm = TRUE)

emails_fails <- round(emails_fails / length(prints$failed), digits = 2)

print(paste0(emails_fails * 100, "%", " patrons inputted email addresses were flagged failed by the program"))
```



#Calculating failed percentage 
```{r}
fails <- sum(prints$failed == "X", na.rm = TRUE)

fail_percent <- round(fails / length(prints$failed), digits = 2)

print(paste0(fail_percent * 100, "%", " of our total print requests failed"))
```


#Calculating how many patrons picked up their prints pf the prints that were completed
```{r}
prints_completed <- filter(prints, print_completed == "X")

picked_up <- sum(prints_completed$picked_up == "X", na.rm = TRUE)

picked_up <- round(picked_up / length(prints$picked_up), digits = 3)

print(paste0("Of the completed print rquests, ", picked_up * 100, "%", " of patrons have picked up their 3D prints"))
```

###### I belive conducting a chisquare test is only going to be useful if we have a lot of color data for each print ###### 

#Chi-sqaure test invesitgating whether print choice has an impact on color choice using a contingency table 
```{r eval=FALSE, include=FALSE}
#A contingency table, also known as a cross-tabulation table or a frequency table, is a table that displays the frequency counts of two or more categorical variables. It shows the distribution of one variable across the levels of another variable.
#In the context of a chi-square test, a contingency table is used to analyze the relationship between two categorical variables. Each cell in the table represents the count or frequency of observations that fall into a specific combination of categories for the variables being analyzed.

prints_filt <- prints %>% filter(print == "Flexi-Unicorn")

cont_table <- table(prints_filt$print, prints_filt$color)

#Actually performing the chi_square test 
chisq.test(cont_table) hehe


#If the p-value is less than the significance level (e.g., 0.05), it indicates that there is a significant relationship between the desired object and the color choice. In such a case, you can conclude that the desired object to be 3D printed has an impact on the color chosen for it.

#Note: The chi-square test assumes that the variables are categorical and the observations are independent. Make sure your data meets these assumptions before applying the test.
```



```{r}
#Saving graphs 

#ggsave(one, file = "C:/Users/Ryan/Coding Projects/KDL Project/3D Printing analysis")
```